\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-09-17 paper.tex
Cleanup fig croquignole expe
Abstract + acknowledgments

\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}

@@

    Blabla

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Examples of \pyRobots actions, mostly extracted from experiments involving
    the PR2 robot.}

@@

We brought two Ranger robots to a kindergarten (17 children, mean age: 3.88
years old, SD=0.65), and after a brief introduction (showing them that removing
the pacifier would ``wake up'' the robot, and putting it back would make it
``fall asleep''), we invited the children to freely play with the robots and
integrate them into their usual games. The experiment lasted 68 minutes.

@@

\begin{figure}
    \resizebox{\columnwidth}{!}{\input{croquignole-expe}}
    \caption{Events fired and actions started per minute, over the 68 min-long
    experiment. The robot sustains an average of 70 actions triggered by minute over
    more than an hour, with peaks at 200 actions/minute.}

@@

\section*{Acknowledgment}

This work has been supported by...

>>>>

\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{booktabs}

@@

Presented is \pyRobots, a new software toolkit for the executive control of
complex robotic systems. Borrowing ideas from previous tools like {\sc
urbi}~\cite{baillie2005urbi}, it proposes a lightweight Python framework to
develop (pre-emptive) concurrent and event-based executive controllers.

Designed in a \emph{bottom-up} fashion, out of the need for a practical,
unobstrusive tool suitable for rapid prototyping of complex interaction
scenarios, \pyRobots also exposes several simple yet convenient abstractions for
physical resources management and pose representation.

Finally, and while middleware-agnostic, it features advanced integration with
the \textit{de-facto} standard ROS middleware.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
    \toprule
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
     \midrule
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
     \midrule
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
     \midrule
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
     \midrule
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
     \bottomrule
\end{tabular}
\end{center}
\caption{Examples of \pyRobots actions, mostly extracted from experiments involving
    the PR2 robot.}

@@

We brought two Ranger robots to a kindergarten (17 children, age: M=3.88,
SD=0.65), and after a brief introduction (showing them that removing the
pacifier would ``wake up'' the robot, and putting it back would make it ``fall
asleep''), we invited the children to freely play with the robots and integrate
them into their usual games. The experiment lasted 68 minutes.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{croquignole-expe}
    \caption{Events fired and actions started per minute, over the 68 min-long
    experiment. The robot sustains an average of 70 actions triggered by minute over
    more than an hour, with peaks at 200 actions/minute.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}

This research was supported by the Swiss National Science Foundation through the
National Centre of Competence in Research Robotics.
